Incentivizing Optimal Forecasting Groups in Prediction Markets

### 2017-04-26 optimal_forecasts/Final Paper/article_2.tex
Resutls for relaxed

>>>>

Now that the framework is capable of reliably eliciting the truthful types from the individual agents, we are able to relax the strict bounds on the value $C$ to allow more individuals to participate and avoid a state where no one participates. To do this, in the simulation, the market organizer will initialize $C$ based on the conventions for the strict incentive scheme. If no agents have an expected positive payoff, decrease the magnitude of $C$. For example, in the simulation algorithm, $C$ was rescaled as so:

\begin{equation}
\label{Cscale}
C = \delta * C
\end{equation}

where $\delta \in \mathbb{R}$ and $0 < \delta < 1$. This need not be the only correct way to scale $C$; as long as $|C'| < |C|$.

\subsubsection{Results for Relaxed Incentive Scheme}
